DOpElib:\\ Differential Equations and Optimization Environment

### 2018-12-16 Examples/OPT/InstatPDE/Example2/content.tex
Added support for time dependent controls and included OPT/InstatPDE/Example3 to show how to use it. Further more, a bug in the functional evaluation has been fixed, up to now it was always assumed that the type ist timelocal. This is now fixed
Updated ControlVector to new common storage Class

This example is a modified version of \texttt{OPT/InstatPDE/Example1}. 
Again, we consider the heat equation, this time with an additional nonlinear
term and most important a time derivative leading to a 
nonstationary optimization problem. The governing equation is
\begin{equation*}
\partial_t u(t,x,y) - \Delta u(t,x,y) = f(t)\cdot q(x,y),
\end{equation*}
with homogeneous Dirichlet-data.
The computational domain is $\Omega \times I = [0,\pi]^2 \times [0,1]$. From the known solution, we can compute the appropriate data 
\begin{align*}
f(t) &= 2,\\
u_0(x,y) &= \sin(x)\sin(y).
\end{align*}

With the cost functional 
\begin{align*}
 \min_{q,u} J(q,u) =&\; \frac{1}{2}\int_{\Omega} \Biggl(u(1,x,y) - \biggl(\frac{2e^2-1}{e^2-1}\biggr)\sin(x) \sin(y)\Biggr)^2\,d(x,y) + \frac{1}{2} \int_{\Omega} q(x,y)^2\,d(x,y).
\end{align*}
It has the optimal solution 
\begin{align*}
\overline{u}(t,x,y) &= \sin(x) \sin(y),\\
\overline{q}(t,x,y) &= \sin(x) \sin(y)
\end{align*}
together with the optimal adjoint state 
\[
 \overline{z}(t,x,y) = \frac{e^2}{1-e^2}e^{2(t-1)}\sin(x) \sin(y).
\]
and the corresponding cost functional value 
\[
J(\overline{q},\overline{u}) = \frac{1}{2} \Bigl(\frac{e^4}{(e^2-1)^2}+1\Bigr)\frac{\pi^2}{4} \approx 2.88382.
\]

\subsubsection{Program description}
In this example, we demonstrate how to implement a control that acts distributed in space and time,
but has no temporal dependence. For this, the control vector type is set to be 
{\texttt ControlType::stationary} (the default for stationary equations). In contrast to 
the case of control in the initial values, the control vector can be accessed at a 
all times.

>>>>

This example is a modified version of \texttt{OPT/InstatPDE/Example1}. 
Again, we consider the heat equation, this time without an additional nonlinear
term. The governing equation is
\begin{equation*}
\partial_t u(t,x,y) - \Delta u(t,x,y) = f(t)\cdot q(x,y),
\end{equation*}
with homogeneous Dirichlet-data.
The computational domain is $\Omega \times I = [0,\pi]^2 \times [0,1]$. From the known solution, we can compute the appropriate data 
\begin{align*}
f(t) &= 2,\\
u_0(x,y) &= \sin(x)\sin(y).
\end{align*}

With the cost functional 
\begin{align*}
 \min_{q,u} J(q,u) =&\; \frac{1}{2}\int_{\Omega} \Biggl(u(1,x,y) - \biggl(\frac{2e^2-1}{e^2-1}\biggr)\sin(x) \sin(y)\Biggr)^2\,d(x,y) + \frac{1}{2} \int_{\Omega} q(x,y)^2\,d(x,y).
\end{align*}
It has the optimal solution 
\begin{align*}
\overline{u}(t,x,y) &= \sin(x) \sin(y),\\
\overline{q}(x,y) &= \sin(x) \sin(y)
\end{align*}
together with the optimal adjoint state 
\[
 \overline{z}(t,x,y) = \frac{e^2}{1-e^2}e^{2(t-1)}\sin(x) \sin(y).
\]
and the corresponding cost functional value 
\[
J(\overline{q},\overline{u}) = \frac{1}{2} \Bigl(\frac{e^4}{(e^2-1)^2}+1\Bigr)\frac{\pi^2}{4} \approx 2.88382.
\]

\subsubsection{Program description}
In this example, we demonstrate how to implement a control that acts distributed in space and time,
but has no temporal dependence. For this, the control vector type is set to be 
{\texttt VectorAction::stationary} (the default for stationary equations). In contrast to 
the case of control in the initial values, the control vector can be accessed at a 
all times.
